Paper Summary

### 2024-11-05 Paper_Summary.Rmd
Added code for data simulation and analysis for Figure 1a. Removed test code and updated the code for Figure 2's data simulation and analysis (with results interpretations). Also added portions of methods summary and statistical methods summary while improving overall formatting.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('ggplot2')
#install.packages('lme4')
#install.packages('lmerTest')
#install.packages('MuMIn')
#install.packages('MASS')
#install.packages('dplyr')
#install.packages('tidyr')
#install.packages('car')
#install.packages('pbkrtest')
#install.packages('pscl')
library(ggplot2)
library(lme4)
library(lmerTest)
library(MuMIn)
library(MASS)
library(dplyr)
library(tidyr)
library(car)
library(pbkrtest)
library(pscl)
```

```{r Assay 1: Figure 1a. Data Simulation & Analysis}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('ggplot2')
#install.packages('lme4')
#install.packages('lmerTest')
#install.packages('MuMIn')
#install.packages('MASS')
#install.packages('dplyr')
#install.packages('tidyr')
#install.packages('car')
#install.packages('pbkrtest')
#install.packages('pscl')
library(ggplot2)
library(lme4)
library(lmerTest)
library(MuMIn)
library(MASS)
library(dplyr)
library(tidyr)
library(car)
library(pbkrtest)
library(pscl)
```
## Data Simulation & Analysis
### Assay 1:
For the data 
```{r Assay 1: Figure 1a. Data Simulation & Analysis}
# Set the number of replicates from paper
n_vials <- 10

# Set the average differences in activity scores
mean_diff_simple <- 6
mean_diff_complex <- -1

# Adjust the standard deviation to achieve the desired t-value and p-value
sd_diff <- 2.5

# Create an empty data frame
activity_data <- data.frame(
  female_type = character(0),
  arena_type = character(0),
  vial_cage_id = numeric(0),
  activity_score = numeric(0)
)

# Generate data for each vial/cage (for loops are harder in R than in Python in my opinion!)
for (i in 1:n_vials) {
  # Simple arena
  activity_data <- rbind(activity_data, data.frame(
    female_type = "large",
    arena_type = "simple",
    vial_cage_id = i,
    activity_score = rnorm(1, mean = 10 + mean_diff_simple/2, sd = sd_diff)
  ))
  activity_data <- rbind(activity_data, data.frame(
    female_type = "small",
    arena_type = "simple",
    vial_cage_id = i,
    activity_score = rnorm(1, mean = 10 - mean_diff_simple/2, sd = sd_diff)
  ))

  # Complex arena
  activity_data <- rbind(activity_data, data.frame(
    female_type = "large",
    arena_type = "complex",
    vial_cage_id = i,
    activity_score = rnorm(1, mean = 10 + mean_diff_complex/2, sd = sd_diff)
  ))
  activity_data <- rbind(activity_data, data.frame(
    female_type = "small",
    arena_type = "complex",
    vial_cage_id = i,
    activity_score = rnorm(1, mean = 10 - mean_diff_complex/2, sd = sd_diff)
  ))
}

# Calculate the difference in activity scores within each vial/cage
activity_data <- activity_data %>%
  group_by(arena_type, vial_cage_id) %>%
  summarize(score_difference = activity_score[female_type == "large"] - activity_score[female_type == "small"])

# Perform the two-sample t-test 
t.test(score_difference ~ arena_type, data = activity_data)
